---
title: "Graphik"
author: "K. Kerkhof, K. Tuteja, A. Wald"
date: "22 2 2020"
output: html_document
---

```{r}
gitter<-(8*8)
l<-1
k<-1
map <- array(0, dim=c(2,gitter))
for (i in 1:gitter) {
      map[1,i] <- k
      map[2,i] <- l
      k<-k+1
      if(k==sqrt(gitter)+1) {
        k<-1
        l<-l+1
      }
}
ordering <- sample.int(size=gitter,n=gitter,replace = FALSE) #give every citiy a number in the first tour

mapplan <- data.frame(x=map[1,],y=map[2,],ordering)
plot(x=mapplan$x,y=mapplan$y,xlab = "",ylab = "",pch=16,cex=0.8,cex.main=1.5,cex.lab=1,cex.axis=0.8,las=1,bty="o")

#mapplan <- mapplan[order(mapplan$ordering),]
mapplan
#data <- read.csv("nrw1379.tsp",header = FALSE,skip = 6,nrows = 1379,sep = "")
#data
#mapplan<- data.frame(x=data$V2,y=data$V3,ordering=data$V1)
#mapplan["ordering"] <- sample.int(size = 1379, n=1379,replace = FALSE)
```

# Distance Calculation

Two functions to calcualte the difference between two points and the hole length of the path through the lattice.
```{r}
distance_two_points <- function(dataframe,x,y){
  return(sqrt((dataframe[x,"x"]-dataframe[y,"x"])^2+(dataframe[x,"y"]-dataframe[y,"y"])^2))
}
distance_overall <- function(dataframe){
  N<-length(dataframe$x)
  distanceold <- 0
  distancenew <- 0
  for (i in 1:N) {
    if(i==N) distancenew <- distance_two_points(dataframe,i,1)
    else distancenew <- distance_two_points(dataframe,i,i+1)
    distanceold <- distanceold + distancenew
  }
  return(distanceold)
}
```

# Estimation of the starting temperature

To estimatet a good starting temperatur $T_s$ we perform an initial random walk at an infinite temperature (all moves are accepted) and measre the occuring Distance differences $\Delta H$ and define the starting temperatur with:  
$T_s = 10\max \{\Delta H\}$  
The temperature is than logarithmically lowered by:  
$T_{new} = \alpha T_{old}$b  
with $\alpha = 0.9$.

```{r}
Value0<-numeric()
Value1<-numeric()
mapplan01 <- mapplan[order(mapplan$ordering),]
SA <- function(dataframe, Temp=100, alpha=0.5){
  N <- length(dataframe$x)
  Sold <- distance_overall(dataframe)
  Snull <-distance_overall(dataframe)
  y <- dataframe
  k <- 0
  while(k < 1){
    for (i in 1:N) {
      first_city <- sample.int(size = 1, n=N)
      second_city <- sample.int(size = 1, n=N)
      while((second_city - first_city)<3 && (second_city<first_city)) {
        first_city <- sample.int(size = 1, n=N)
        second_city <- sample.int(size = 1, n=N)
      }
      ordering_first_city <- y[first_city,"ordering"]
      ordering_second_city <-y[second_city,"ordering"]
      old_order <- y[(first_city):(second_city),"ordering"]
      #print(first_city)
      #print(second_city)
      #print(old_order)
      new_older <- rev(old_order)
      #print(y[first_city:second_city,"ordering"])
      y[(first_city):(second_city),"ordering"] <- new_older
      #print(new_older)
      #print(y[first_city-1:second_city+1,"ordering"])
      #y[first_city,"ordering"] <- y[second_city,"ordering"]
      #y[second_city,"ordering"] <- ordering_first_city
      #print(y[first_city:second_city,"ordering"])
      #y[,"ordering"]<-c(1:100)
      #print(y[,"ordering"])
      y <- y[order(y$ordering),]
      #print(y[,"ordering"])
      #print(y)
      Snew <- distance_overall(y)
      accept <- FALSE
      if (Snew < Sold) accept <- TRUE
      else accept <-TRUE
      if (accept){
        dataframe <- y
        Sold <- Snew
      }
      else{
        y <- dataframe
      }
    }
    k <- k+1
    Value0 <- append(Value0, Sold)
    Value1 <-append(Value1,abs(Snull-Sold))
  }
  erg <- list(Value0=Value0,Value1=Value1)
  return(erg)
}
delta_H <- numeric()
for (i in 1:10) {
  delta_H <- append(delta_H,SA(mapplan01))
}
```
Getting the starting temperature:
```{r}
T_s =10*max(delta_H$Value1)
T_s
T_middle = 1/10*max(delta_H$Value1)
T_middle
T_end <- T_middle*10^(-3)
T_end
```
```{r}
erste_Ordnung <- mapplan[order(mapplan$ordering),]
distance_overall(erste_Ordnung)
```

Now the calculation of the shortest path can occur:
```{r}
Path <- numeric()
Mittelwerte <- numeric()
Akzeptanzrate_temp_all<-numeric()
Akzeptanzrate_temp_Temp_all<-numeric()
Akzeptanzrate_echt_all<-numeric()
Akzeptanzrate_echt_Temp_all<-numeric()

Akzeptanzrate_temp_allmean<-numeric()
Akzeptanzrate_temp_Temp_allmean<-numeric()
Akzeptanzrate_echt_allmean<-numeric()
Akzeptanzrate_echt_Temp_allmean<-numeric()

Varianzen <- numeric()
Temperaturen <- numeric()
Zwischenspeicher_x<-numeric()
Zwischenspeicher_y<-numeric()
Zwischenspeicher_ordering<-numeric()
Abweichung <- 1000
SA_new <- function(dataframe, Temp=T_s){
  alpha <- 0.99
  N <- length(dataframe$x)
  Sold <- distance_overall(dataframe)
  y <- dataframe
  k <- 0
  iter <- 0
  Kuchen<-gitter
  while((Sold-gitter)/gitter>0.15){
    
 #   if(Temp>100) {
#      alpha <- 0.8
#     Kuchen <-10
#   }
#    else if(Temp<=100 && Temp>=0.1) {
#      alpha <- 0.998
#      Kuchen <-100
#    }
#    else if(Temp<0.1) {
#      alpha <- 0.8
#      Kuchen <-10
#    }
    
    S_first <- distance_overall(dataframe)
    
Akzeptanzrate_echt <- numeric()
Akzeptanzrate_echt_Temp <- numeric()
Akzeptanzrate_temp <- numeric()
Akzeptanzrate_temp_Temp <- numeric()
    
    for (i in 1:1) {
      Speicher_frame <- dataframe
      y<-dataframe
      Sold <- distance_overall(dataframe)
      Akzeptor_echt <- TRUE
      Akzeptor_temp <- TRUE
      for (j in 1:Kuchen) {
        if(Akzeptor_echt){
          Start_accept_echt <- as.double(Sys.time())
          Akzeptor_echt <- FALSE
        }
        if(Akzeptor_temp){
          Start_accept_temp <- Start_accept_echt
          Akzeptor_temp <- FALSE
        }
        first_city <- sample.int(size = 1, n=N)
        second_city <- sample.int(size = 1, n=N)
        while((second_city - first_city)<3 && (second_city<first_city)) {
        first_city <- sample.int(size = 1, n=N)
        second_city <- sample.int(size = 1, n=N)
        }
        ordering_first_city <- y[first_city,"ordering"]
        ordering_second_city <-y[second_city,"ordering"]
        old_order <- y[(first_city):(second_city),"ordering"]
        #print(first_city)
        #print(second_city)
        #print(old_order)
        new_older <- rev(old_order)
        #print(y[first_city:second_city,"ordering"])
        y[(first_city):(second_city),"ordering"] <- new_older
        #print(new_older)
        #print(y[first_city-1:second_city+1,"ordering"])
        #y[first_city,"ordering"] <- y[second_city,"ordering"]
        #y[second_city,"ordering"] <- ordering_first_city
        #print(y[first_city:second_city,"ordering"])
        #y[,"ordering"]<-c(1:100)
        #print(y[,"ordering"])
        y <- y[order(y$ordering),]
        #print(y[,"ordering"])
        #print(y)
        Snew <- distance_overall(y)
        accept <- FALSE

        if (Snew < Sold){
          accept <- TRUE
          Akzeptor_echt <- TRUE
          Ende <- as.double(Sys.time())
          Akzeptanzrate_echt <- append(Akzeptanzrate_echt, Ende - Start_accept_echt)
          Akzeptanzrate_echt_Temp <- append(Akzeptanzrate_echt_Temp, Temp)
        }
        else if (runif(1) < exp((Sold-Snew)/Temp)){ 
          accept <-TRUE
          Akzeptor_temp <- TRUE
          Ende <- as.double(Sys.time())
          Akzeptanzrate_temp <- append(Akzeptanzrate_temp, Ende - Start_accept_temp)
          Akzeptanzrate_temp_Temp <- append(Akzeptanzrate_temp_Temp, Temp)
        }
        if (accept){
          dataframe <- y
          Sold <- Snew
        }
        else{
          y <- dataframe
        }
      }
    Path<-append(Path,Sold)
    Zwischenspeicher_ordering <- append(Zwischenspeicher_ordering,dataframe[,"ordering"])
    Zwischenspeicher_x<-append(Zwischenspeicher_x,dataframe[,"x"])
    Zwischenspeicher_y<-append(Zwischenspeicher_y,dataframe[,"y"])
    dataframe <-Speicher_frame
    }
    Akzeptanzrate_temp_allmean<-append(Akzeptanzrate_temp_allmean,mean(Akzeptanzrate_temp))
    Akzeptanzrate_temp_Temp_allmean<-append(Akzeptanzrate_temp_Temp_allmean,mean(Akzeptanzrate_temp_Temp))
    Akzeptanzrate_echt_allmean<-append(Akzeptanzrate_echt_allmean,mean(Akzeptanzrate_echt))
    Akzeptanzrate_echt_Temp_allmean<-append(Akzeptanzrate_echt_Temp_allmean,mean(Akzeptanzrate_echt_Temp))
    
    Mittelwerte <- append(Mittelwerte,mean(Path))
    Varianzen <- append(Varianzen,var(Path))
    Temperaturen <- append(Temperaturen,Temp)
    dataframe[,"ordering"] <- Zwischenspeicher_ordering
    dataframe[,"x"] <- Zwischenspeicher_x
    dataframe[,"y"] <- Zwischenspeicher_y
    Sold<-Path
   
    #dataframe<-dataframe[order(dataframe$start_position, dataframe$ordering),]
    Abweichung <- 1000
    print(Path)
    #print(Sold)
    
    Path<-numeric()
    
    Zwischenspeicher_x<-numeric()
    Zwischenspeicher_y<-numeric()
    Zwischenspeicher_start<-numeric()
    Zwischenspeicher_ordering<-numeric()
    
    Temp <- Temp*alpha
    k <- k+1
    print(Temp)
  }
  df <- data.frame(Temperaturen = Temperaturen ,Mittelwerte=Mittelwerte,Varianzen=Varianzen,Akzeptanzrate_echt_allmean=Akzeptanzrate_echt_allmean, Akzeptanzrate_echt_Temp_allmean=Akzeptanzrate_echt_Temp_allmean, Akzeptanzrate_temp_allmean=Akzeptanzrate_temp_allmean, Akzeptanzrate_temp_Temp_allmean=Akzeptanzrate_temp_Temp_allmean)
 # write.csv(df, "nrw1379_Lin_2_opt_OV.txt",row.names = FALSE)
  #write.csv(dataframe,"nrw1379_Lin_2_opt_Path_OV.txt",row.names = FALSE)
  erg <- list(dataframe=dataframe, Mittelwerte=Mittelwerte, Varianzen=Varianzen, Temperaturen=Temperaturen,Akzeptanzrate_echt_all=Akzeptanzrate_echt_all, Akzeptanzrate_echt_Temp_all=Akzeptanzrate_echt_Temp_all, Akzeptanzrate_temp_all=Akzeptanzrate_temp_all, Akzeptanzrate_temp_Temp_all=Akzeptanzrate_temp_Temp_all,Akzeptanzrate_echt_allmean=Akzeptanzrate_echt_allmean, Akzeptanzrate_echt_Temp_allmean=Akzeptanzrate_echt_Temp_allmean, Akzeptanzrate_temp_allmean=Akzeptanzrate_temp_allmean, Akzeptanzrate_temp_Temp_allmean=Akzeptanzrate_temp_Temp_allmean)
  return(erg)
}
```

```{r}
mapplan_in_use <- mapplan[order(mapplan$ordering),]
```

```{r}
Zeit_start <- as.double(Sys.time())
erg<-SA_new(mapplan_in_use)
Ende <- as.double(Sys.time()) - Zeit_start
print(Ende)
```

```{r}
plot(erg$Akzeptanzrate_echt_Temp_allmean,1/erg$Akzeptanzrate_echt_allmean, pch=16,cex=0.8,log="x",col="blue")
points(erg$Akzeptanzrate_temp_Temp_allmean, 1/erg$Akzeptanzrate_temp_allmean, pch=16,cex=0.8,col="red")
```


```{r}

ordered_mapplan <- erg$dataframe
plot(x=erg$Temperaturen,y=erg$Mittelwerte,xlab = "temperature T",ylab = "Distance",main="",pch=16,cex=0.8,cex.main=1.5,cex.lab=1,cex.axis=0.8,las=1,bty="o",log="x")
#axis(1,at=c(1e-5,1e-3,1e-1,1e1,1e2),labels = c("0.00001","0.001","0.1","10","1000"))

```
```{r}
# length(ordered_mapplan$x)
plot(x=ordered_mapplan$x,y=ordered_mapplan$y,xlab = "x",ylab = "y",main="Path",pch=16,cex=0.8,cex.main=1.5,cex.lab=1,cex.axis=0.8,las=1,bty="o")
#pch type of the points
# cex size of the points
# las upright labels


s <- seq(length(ordered_mapplan$x)-1)
arrows(ordered_mapplan$x[s],ordered_mapplan$y[s],ordered_mapplan$x[s+1],ordered_mapplan$y[s+1],length = 0.08,angle = 25, lwd = 1.5)
arrows(ordered_mapplan$x[length(ordered_mapplan$x)],ordered_mapplan$y[length(ordered_mapplan$x)],ordered_mapplan$x[1],ordered_mapplan$y[1],length = 0.08,angle = 25, lwd = 1.5)

#lty linetype 
# 1 = straight line 2= dotted 3 = smaller dotted
#lwd linewith
erg$Mittelwerte[length(erg$Mittelwerte)]
length(erg$Mittelwerte)
```



