---
title: "Graphik"
author: "K. Kerkhof, K.Tuteja, A.Wald"
date: "22 2 2020"
output: html_document
---

#```{r}
gitter<-(14*14)
l<-1
k<-1
map <- array(0, dim=c(2,gitter))
for (i in 1:gitter) {
      map[1,i] <- k
      map[2,i] <- l
      k<-k+1
      if(k==sqrt(gitter)+1) {
        k<-1
        l<-l+1
      }
}
ordering <- sample.int(size=gitter,n=gitter,replace = FALSE) #give every citiy a number in the first tour

mapplan <- data.frame(x=map[1,],y=map[2,],ordering)
plot(x=mapplan$x,y=mapplan$y,xlab = "",ylab = "",pch=16,cex=0.8,cex.main=1.5,cex.lab=1,cex.axis=0.8,las=1,bty="o")
#```
```{r}
#mapplan <- mapplan[order(mapplan$ordering),]
#mapplan
data <- read.csv("TSP.txt",sep = "")
data2 <-as.matrix(data)
#data
#mapplan<- data.frame(x=data$V2,y=data$V3,ordering=data$V1)
#mapplan["ordering"] <- sample.int(size = 1379, n=1379,replace = FALSE)
data2
#data2[11,1]
#sqrt(length(data2))
#sortierung <- c(1:11)
#sortierung
#sortierung<-c(sortierung[-4],sortierung[4])

#switches <- sample.int(11,2,replace = FALSE)
#print(switches)
#if(switches[1]<switches[2]) extract <- sortierung[switches[1]:switches[2]]
#if(switches[2]<switches[1]) extract <- sortierung[switches[2]:switches[1]]
#extract <- rev(extract)

#extract
#sortierung<- which()
#sortierung
#sortierung<-swtch(sortierung,switches[1],switches[2])
#sortierung
#new_data <- data2[sortierung,sortierung]
#new_data
```

# Distance Calculation

Two functions to calcualte the difference between two points and the hole length of the path through the lattice.


```{r}
distance_overal_matrix <-function(matrix){
  N<- sqrt(length(matrix))
  sum_all <-0
  sum_new <-0
  for (i in 1:(N-1)) {
    sum_new <- matrix[i,i+1]
    sum_all <- sum_all + sum_new
  }
  sum_all <- sum_all + matrix[N,1]
  return(sum_all)
}

swtch <- function(x,i,j) {x[c(i,j)] <- x[c(j,i)]; x}
```

# Estimation of the starting temperature

To estimatet a good starting temperatur $T_s$ we perform an initial random walk at an infinite temperature (all moves are accepted) and measre the occuring Distance differences $\Delta H$ and define the starting temperatur with:  
$T_s = 10\max \{\Delta H\}$  
The temperature is than logarithmically lowered by:  
$T_{new} = \alpha T_{old}$b  
with $\alpha = 0.9$.

```{r}
Value0<-numeric()
Value1<-numeric()
SA <- function(matrix, Temp=100, alpha=0.5){
  N <- sqrt(length(matrix))
  Sold <- distance_overal_matrix(matrix)
  Snull <-distance_overal_matrix(matrix)
  y <- matrix
  k <- 0
  sortierung <- c(1:N)
  while(k < 1){
    for (i in 1:100) {
      switches <- sample.int(N,2,replace = FALSE)
      #print(N)
      #print(place)
      sortierung<-swtch(sortierung,switches[1],switches[2])
     
      #print(ordering)
      y <- y[sortierung,sortierung]
      Snew <- distance_overal_matrix(y)
      accept <- FALSE
      if (Snew < Sold) accept <- TRUE
      else accept <-TRUE
      if (accept){
        matrix <- y
        Sold <- Snew
      }
      else{
        y <- matrix
      }
    }
    k <- k+1
    Value0 <- append(Value0, Sold)
    Value1 <-append(Value1,abs(Snull-Sold))
  }
  erg <- list(Value0=Value0,Value1=Value1,matrix=matrix)
  return(erg)
}
delta_H <- numeric()
for (i in 1:10) {
  delta_H <- append(delta_H,SA(data2))
}
```
Getting the starting temperature:
```{r}
T_s =10*max(delta_H$Value1)
T_s
T_middle = 1/10*max(delta_H$Value1)
T_middle
T_end <- T_middle*10^(-3)
T_end
```
```{r}
delta_H$matrix
distance_overal_matrix(delta_H$matrix)
```

Now the calculation of the shortest path can occur:
```{r}
Path <- numeric()
Mittelwerte <- numeric()
Varianzen <- numeric()
Temperaturen <- numeric()
Abweichung <- 1000
SA_new <- function(matrix, Temp=1000){
  alpha <- 0.99
  N <- sqrt(length(matrix))
  sortierung <- c(1:N)
  Sold <- distance_overal_matrix(matrix)
  y <- matrix
  k <- 0
  iter <- 0
  Kuchen<-1000
  while(Temp>=0.001){
    
 #   if(Temp>100) {
#      alpha <- 0.8
#     Kuchen <-10
#   }
#    else if(Temp<=100 && Temp>=0.1) {
#      alpha <- 0.998
#      Kuchen <-100
#    }
#    else if(Temp<0.1) {
#      alpha <- 0.8
#      Kuchen <-10
#    }
    
    S_first <- distance_overal_matrix(matrix)
    
    for (i in 1:1) {
      Speicher_frame <- matrix
      y<-matrix
      Sold <- distance_overal_matrix(matrix)

      for (j in 1:Kuchen) {
      
        switches <- sample.int(N,2,replace = FALSE)
        #print(N)
        #print(place)
        sortierung<-swtch(sortierung,switches[1],switches[2])
        #print(ordering)
        y <- y[sortierung,sortierung]
        Snew <- distance_overal_matrix(y)
        accept <- FALSE

        if (Snew < Sold){
          accept <- TRUE
          best_way <- sortierung
        }
        else if (runif(1) < exp((Sold-Snew)/Temp)){ 
          accept <-TRUE
        }
        if (accept){
         matrix <- y
          Sold <- Snew
          
        }
        else{
          y <- matrix
        }
      }
    Path<-append(Path,Sold)
   
    }
    Mittelwerte <- append(Mittelwerte,mean(Path))
    Varianzen <- append(Varianzen,var(Path))
    Temperaturen <- append(Temperaturen,Temp)
    Sold<-Path
    #print(Path)
    #print(Sold)
    Path<-numeric()
    Temp <- Temp*alpha
    k <- k+1
    print(Temp)
  }
  df <- data.frame(Temperaturen = Temperaturen ,Mittelwerte=Mittelwerte,Varianzen=Varianzen)
 # write.csv(df, "nrw1379_Lin_2_opt_OV.txt",row.names = FALSE)
  #write.csv(dataframe,"nrw1379_Lin_2_opt_Path_OV.txt",row.names = FALSE)
  erg <- list(best_way=best_way, Mittelwerte=Mittelwerte, Varianzen=Varianzen, Temperaturen=Temperaturen,matrix=y)
  return(erg)
}
```

```{r}
Zeit_start <- as.double(Sys.time())
erg<-SA_new(data2)
Ende <- as.double(Sys.time()) - Zeit_start
print(Ende)
```


```{r}
plot(x=erg$Temperaturen,y=erg$Mittelwerte,xlab = "temperature T",ylab = "Distance",main="",pch=16,cex=0.8,cex.main=1.5,cex.lab=1,cex.axis=0.8,las=1,bty="o",log="x")
#axis(1,at=c(1e-5,1e-3,1e-1,1e1,1e2),labels = c("0.00001","0.001","0.1","10","1000"))
erg$Mittelwerte[length(erg$Mittelwerte)]
```
```{r}
#data2
#erg$best_way
#ordered_data <- data2[erg$best_way,erg$best_way]
#ordered_data
#distance_overal_matrix(data2)
#distance_overal_matrix(ordered_data)
erg$matrix
distance_overal_matrix(erg$matrix)
```




